My title

### 2024-12-03 paper/paper.qmd
updated measurement

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(here)
library(readr)
library(usethis)
library(dplyr)
library(testthat)
library(rstanarm)
library(ggplot2)
library(brms)

@@

I used the statistical programming language R [@citeR] for data cleaning and analysis. The R packages used were

@@

@@

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

>>>>

library(tidyverse)
library(arrow)
library(here)
library(readr)
library(usethis)
library(dplyr)
library(testthat)
library(rstanarm)
library(ggplot2)
library(brms)

@@

This study uses the [@airraids]

I used the statistical programming language R [@citeR] for data cleaning and analysis. The R packages used were **`tidyverse`** for data manipulation and visualization [@tidyverse], **`here`** for file path management [@here], **`lubridate`** for date handling [@lubridate], **`arrow`** for data storage and processing [@arrow], **`testthat`** for unit testing [@testthat], **`readr`** for reading structured data [@readr], **`dplyr`** for data manipulation [@dplyr], **`stringr`** for string operations [@stringr], **`ggplot2`** for creating visualizations [@ggplot2], **`caret`** for modeling [@caret], **`kableExtra`** for creating tables [@kableExtra], and **`modelsummary`** for summarizing models and results [@modelsummary].

@@

arrow /
here / 
readr /
usethis
dplyr / 
testthat / 
rstanarm
ggplot2 /
brms

@@

The measurement process refers to the attempt to explain real world events through data, such as an individual act of warfare, as represented by the use of a self-propelled (missile) or gravity released explosive (bomb) to strike land or sea target, into numerical entries describing this event. Each entry in the dataset represents a bombing incident that took place in the UK during WW2.
